Variational Monte Carlo on bosonic systems

### 2018-02-20 project_1/article/article.tex

\documentclass[
    a4paper, aps, twocolumn, floatfix, superscriptaddress]{revtex4-1}

@@

\begin{abstract}
    Something very abstract and clever should go here.
\end{abstract}

@@

        \subsubsection{Non-interacting harmonic oscillator}
            We start by finding an analytical expression for the local energy in
            a system where we set $a = 0$ and $\beta = 1$, i.e., a system of
            non-interacting harmonic oscillators.
            \begin{align}
                \Psi_T(\vf{r})
                = \Phi_T(\vf{r})
                = \prod_i^N \exp\bigl[
                    -\alpha |\vf{r}_i|^2
                \bigr],
            \end{align}
            where $|\vf{r}_i| = r_i$. As $a = 0$ the interaction term,
            $w(\vf{r}_i, \vf{r}_j)$, vanishes and the Hamiltonian is given by
            (in the spherical case)
            \begin{align}
                H &= \sum_i^N h(\vf{r}_i)
                = \sum_i^N \Biggl(
                    -\frac{\hbar^2}{2m}\nabla_i^2
                    + \half m \omega^2 r_i^2
                \Biggr).
            \end{align}
            The hardest part of finding the local energy is computing the
            kinetic term. Starting with the gradient of the wavefunction in the
            non-interacting case, we get
            \begin{align}
                \nabla_k\Psi_T(\vf{r})
                &= -2\alpha \vf{r}_k\Psi_T(\vf{r}).
            \end{align}
            The Laplacian yields
            \begin{align}
                \nabla^2_k\Psi_T(\vf{r})
                &= \big(-2d\alpha + 4\alpha^2 r_k^2\bigr)\Psi_T(\vf{r}),
            \end{align}
            where $d$ is the dimensionality of the problem determined by
            $\vf{r}_k \in \mathbb{R}^d$. This yields the analytical expression
            for the local energy in the non-interacting case to be
            \begin{align}
                E_L(\vf{r})
                &=
                \sum_i^N
                \Biggl(
                    -\frac{\hbar^2}{2m}
                    \bigl[
                        -2d\alpha + 4\alpha^2 r_i^2
                    \bigr]
                    + \half m\omega^2 r_i^2
                \Biggr).
            \end{align}
            In natural units, with $\hbar = c = m = 1$, this reduces to
            \begin{align}
                E_L(\vf{r})
                &=
                \alpha dN
                + \biggl(
                    \half\omega^2
                    - 2\alpha^2
                \biggr)
                \sum_i^N r_i^2.
            \end{align}
            It is worth noting that for $\omega = 1$ we will find a stable value
            for the local energy when $\alpha = \half$. This happens as the
            entire sum over all the random walkers disappears.

%            Working in spherical coordinates the gradient and the Laplace
%            operator (applied to a scalar function) becomes
%            \begin{align}
%                \nabla f
%                &= \vf{e}_r\tpl{r}f
%                + \vf{e}_{\theta}\frac{1}{r}\tpl{\theta}f
%                + \vf{e}_{\phi}\frac{1}{r\sin(\theta)}\tpl{\phi}f, \\
%                \nabla^2 f
%                &= \frac{1}{r^2}\tpl{r}
%                \bigl[
%                    r^2\tpl{r}f
%                \bigr]
%                + \frac{1}{r^2\sin(\theta)}\tpl{\theta}
%                \bigl[
%                    \sin(\theta)\tpl{\theta}f
%                \bigr] \nonumber\\
%                &\qquad
%                + \frac{1}{r^2\sin^2(\theta)}\tpl{\phi}^2f,
%            \end{align}
%            where $\vf{e}_r$ signifies the unit vector in the radial direction
%            and we use the shorthand notation
%            \begin{align}
%                \tpl{r}f \equiv \dpd[]{f}{r}.
%            \end{align}
%            As the trial wavefunction for $\beta = 1$ is purely radial we get
%            the same expression in one, two and three dimensions by setting
%            \begin{align}
%                r^2 =
%                \begin{cases}
%                    x^2 & \text{one dimension}, \\
%                    x^2 + y^2 & \text{two dimensions}, \\
%                    x^2 + y^2 + z^2 & \text{three dimensions}.
%                \end{cases}
%            \end{align}
%            The gradient then becomes
%            \begin{align}
%                \nabla_i\bra{\vf{r}}\ket{\Psi_T}
%                &= \vf{e}_{{r_i}}\tpl{{r_i}}\prod_j^N\exp\bigl[
%                    -\alpha r_j^2
%                \bigr] \\
%                &=
%                -2\alpha r_i\prod_j^N\exp\bigl[
%                    -\alpha r_j^2
%                \bigr]\vf{e}_{{r_i}} \\
%                &=
%                -2\alpha r_i\bra{\vf{r}}\ket{\Psi_T}\vf{e}_{{r_i}}.
%            \end{align}
%            The Laplacian is given by
%            \begin{align}
%                \nabla_i^2\bra{\vf{r}}\ket{\Psi_T}
%                &= \frac{1}{r_i^2}\tpl{{r_i}}
%                \biggl\{
%                    r_i^2\tpl{{r_i}}
%                    \prod_j^N\exp\bigl[
%                        -\alpha r_j^2
%                    \bigr]
%                \biggr\} \\
%                &=
%                \frac{1}{r_i^2}\tpl{{r_i}}
%                \biggl\{
%                    -2 \alpha r_i^3
%                    \prod_j^N\exp\bigl[
%                        -\alpha r_j^2
%                    \bigr]
%                \biggr\} \\
%                &=
%                \frac{1}{r_i^2}
%                \Bigl\{
%                    -6 \alpha r_i^2
%                    + 4\alpha^2 r_i^4
%                \Bigr\}
%                \prod_j^N\exp\bigl[
%                    -\alpha r_j^2
%                \bigr]
%                \\
%                &=
%                \Bigl\{
%                    -6 \alpha
%                    + 4\alpha^2 r_i^2
%                \Bigr\}
%                \bra{\vf{r}}\ket{\Psi_T}.
%            \end{align}
%            This gives the analytical expression for the local energy to be
%            \begin{align}
%                E_L(\vf{r})
%                &= \frac{\bra{\vf{r}}H\ket{\Psi_T}}{\bra{\vf{r}}\ket{\Psi_T}} \\
%                &= \sum_i^N \Bigl(
%                    4\alpha^2 r_i^2
%                    + \half m \omega^2 r_i^2
%                \Bigr) - 6\alpha.
%            \end{align}
%            The \textit{drift force} of the system is given by
%            \begin{align}
%                \vf{F}_i
%                &=
%                \frac{2\nabla_i\bra{\vf{r}}\ket{\Psi_T}}
%                {\bra{\vf{r}}\ket{\Psi_T}} \\
%                &= -4\alpha r_i\vf{e}_{{r_i}}.
%            \end{align}

@@

            %    We can now find the Laplacian of the trial wavefunction. This
            %    gives
            %    \begin{align}
            %        \nabla_k^2\bra{\vf{r}}\ket{\Psi_T}
            %        &= \nabla_k\nabla_k\bra{\vf{r}}\ket{\Psi_T}
            %        = \nabla_k
            %        \Biggl(
            %            \frac{\nabla_k\phi(\vf{r}_k)}{\phi(\vf{r}_k)}
            %            +
            %            \sum_{m \neq k}^N\nabla_k u(r_{km})
            %        \Biggr)
            %        \bra{\vf{r}}\ket{\Psi_T} \\
            %        &=
            %        \Biggl(
            %            \frac{\nabla_k^2\phi(\vf{r}_k)}{\phi(\vf{r}_k)}
            %            + \left[
            %                \nabla\frac{1}{\phi(\vf{r}_k)}
            %            \right]
            %            \nabla_k\phi(\vf{r}_k)
            %            +
            %            \sum_{m \neq k}^N\nabla_k^2 u(r_{km})
            %        \Biggr)
            %        \bra{\vf{r}}\ket{\Psi_T}
            %        \\
            %        &\qquad
            %        +
            %        \Biggl(
            %            \frac{\nabla_k\phi(\vf{r}_k)}{\phi(\vf{r}_k)}
            %            +
            %            \sum_{m \neq k}^N\nabla_k u(r_{km})
            %        \Biggr)
            %        \nabla_k\bra{\vf{r}}\ket{\Psi_T} \\
            %        &=
            %        \Biggl(
            %            \frac{\nabla_k^2\phi(\vf{r}_k)}{\phi(\vf{r}_k)}
            %            - \left[
            %                \frac{\nabla_k\phi(\vf{r}_k)}{\phi(\vf{r}_k)}
            %            \right]^2
            %            +
            %            \sum_{m \neq k}^N\nabla_k^2 u(r_{km})
            %        \Biggr)
            %        \bra{\vf{r}}\ket{\Psi_T}
            %        \\
            %        &\qquad
            %        +
            %        \Biggl(
            %            \frac{\nabla_k\phi(\vf{r}_k)}{\phi(\vf{r}_k)}
            %            +
            %            \sum_{m \neq k}^N\nabla_k u(r_{km})
            %        \Biggr)^2
            %        \bra{\vf{r}}\ket{\Psi_T}.
            %    \end{align}
            %    We now divide by the trial wavefunction. This simplifies the
            %    calculations and is more similar to the expression for the local
            %    energy.
            %    \begin{align}
            %        \frac{\nabla_k^2\bra{\vf{r}}\ket{\Psi_T}}
            %        {\bra{\vf{r}}\ket{\Psi_T}}
            %        &=
            %        \frac{\nabla_k^2\phi(\vf{r}_k)}{\phi(\vf{r}_k)}
            %        - \left[
            %            \frac{\nabla_k\phi(\vf{r}_k)}{\phi(\vf{r}_k)}
            %        \right]^2
            %        +
            %        \sum_{m \neq k}^N\nabla_k^2 u(r_{km})
            %        +
            %        \Biggl(
            %            \frac{\nabla_k\phi(\vf{r}_k)}{\phi(\vf{r}_k)}
            %            +
            %            \sum_{m \neq k}^N\nabla_k u(r_{km})
            %        \Biggr)^2 \\
            %        &=
            %        \frac{\nabla_k^2\phi(\vf{r}_k)}{\phi(\vf{r}_k)}
            %        +
            %        \sum_{m \neq k}^N\nabla_k^2 u(r_{km})
            %        +
            %        \frac{2\nabla_k\phi(\vf{r}_k)}{\phi(\vf{r}_k)}
            %        \sum_{m \neq k}^N\nabla_k u(r_{km})
            %        +
            %        \Biggl(
            %            \sum_{m \neq k}^N\nabla_k u(r_{km})
            %        \Biggr)^2
            %    \end{align}

@@

                    %\nonumber \\
                    %&\qquad

@@

            %component for particle $k$ by
            %\begin{align}
            %    \tpl{{r_k}}
            %    = \dpd[]{r_{km}}{r_k}\tpl{{r_{km}}}.
            %\end{align}
            %The derivative of the distance $r_{km}$ is given by
            %\begin{gather}
            %    r_{km} = |\vf{r}_k - \vf{r}_m|
            %    \implies
            %    \dpd[]{r_{km}}{r_k}
            %    = \frac{r_k - r_m}{|\vf{r}_k - \vf{r}_m|},
            %\end{gather}
            %where in spherical coordinates $\vf{r}_k = r_k\vf{e}_r$.  The
            %gradient of $u(r_{km})$ thus simplifies to only include the radial
            %contribution.
            %\begin{align}
            %    \nabla_k u(r_{km})
            %    &=
            %    \vf{e}_{r}\tpl{{r_k}}u(r_{km})
            %    \\
            %    &=
            %    \vf{e}_r\dpd[]{r_{km}}{r_k}\tpl{{r_{km}}}u(r_{km})
            %    \\
            %    &= \vf{e}_r\frac{r_k - r_m}{r_{km}}
            %    \tpl{{r_{km}}}u(r_{km}).
            %\end{align}
            %    Using this expression we find the Laplacian to be
            %    \begin{align}
            %        \nabla_k^2 u(r_{km})
            %        &=
            %        \frac{1}{r_{km}} \tpl{{r_{km}}} u(r_{km})
            %        + \frac{(r_k - r_m)^2}{r_{km}^3} \tpl{{r_{km}}} u(r_{km})
            %        +
            %        \frac{r_k - r_m}{r_{km}}
            %        \dpd[]{r_{km}}{r_k}
            %        \partial_{{r_{km}}}^2 u(r_{km}) \\
            %        &=
            %        \frac{1}{r_{km}} \tpl{{r_{km}}} u(r_{km})
            %        + \frac{r_{km}^2}{r_{km}^3} \tpl{{r_{km}}} u(r_{km})
            %        +
            %        \frac{(r_k - r_m)^2}{r_{km}^2}
            %        \partial_{{r_{km}}}^2 u(r_{km}) \\
            %        &=
            %        \frac{2}{r_{km}}\tpl{{r_{km}}}u(r_{km})
            %        + \partial_{{r_{km}}}^2u(r_{km}).
            %    \end{align}
            %We now take the derivate with respect to $r_{km}$ of the interaction
            %functions $u(r_{km})$ to find the closed form expressions. We get
            %\begin{align}
            %    \partial_{r_{km}}u(r_{km})
            %    &=
            %    \partial_{r_{km}}
            %    \ln\Biggl(
            %        1 - \frac{a}{r_{km}}
            %    \Biggr) \\
            %    &=
            %    \partial_{r_{km}}
            %    \ln\Biggl(
            %        \frac{1}{r_{km}}
            %        (r_{km} - a)
            %    \Biggr) \\
            %    &=
            %    \partial_{r_{km}}
            %    \Bigl[
            %        \ln(r_{km} - a)
            %        - \ln(r_{km})
            %    \Bigr] \\
            %    &=
            %    \frac{1}{r_{km} - a} - \frac{1}{r_{km}} \\
            %    &=
            %    \frac{a}{r_{km}(r_{km} - a)} \\
            %    \partial_{r_{km}}^2u(r_{km})
            %    &= a\Bigl(
            %        \partial_{r_{km}}\frac{1}{r_{km}}
            %    \Bigr)
            %    \partial_{r_{km}}\frac{1}{r_{km} - a}
            %    \nonumber \\
            %    &\qquad
            %    + a\frac{1}{r_{km}}
            %    \Bigl(
            %        \partial_{r_{km}}\frac{1}{r_{km} - a}
            %    \Bigr) \\
            %    &=
            %    -\frac{a}{r_{km}^2(r_{km} - a)}
            %    -\frac{a}{r_{km}(r_{km} - a)^2} \\
            %    &=
            %    - \frac{2a(r_{km} - 1)}{r_{km}^2(r_{km} - a)^2}.
            %\end{align}
            %Using this we are now able to write the closed form expression of
            %the Laplacian of the trial wavefunction.
            %    \begin{align}
            %        \frac{\nabla_k^2\bra{\vf{r}}\ket{\Psi_T}}
            %        {\bra{\vf{r}}\ket{\Psi_T}}
            %        &=
            %        -2\alpha
            %        \big(
            %            2 + \beta
            %        \bigr)
            %        + 4\alpha^2
            %        \bigl(
            %            x_k^2 + y_k^2 + \beta^2z_k^2
            %        \bigr)
            %        %\nonumber \\
            %        %&\qquad
            %        +
            %        2a
            %        \sum_{m \neq k}^N
            %        \Biggl[
            %            \frac{1}{r_{km}^2(r_{km} - a)}
            %            - \frac{r_{km} - 1}{r_{km}^2(r_{km} - a)^2}
            %        \Biggr]
            %        \nonumber \\
            %        &\qquad
            %        -4\alpha(x_k\vf{e}_i + y_k\vf{e}_j + \beta z_k\vf{e}_k)
            %        \cdot
            %        a\sum_{m \neq k}^N
            %        \frac{\vf{r}_k - \vf{r}_m}{r_{km}^2(r_{km} - a)}
            %        + \Biggl[
            %            a\sum_{m \neq k}^N
            %            \frac{\vf{r}_k - \vf{r}_m}{r_{km}^2(r_{km} - a)}
            %        \Biggr]^2.
            %    \end{align}
            %To ease the load on the CPU we try to restrict the number of times
            %we evaluate the sums. For brevity we introduce the following
            %functions
            %\begin{align}
            %    \xi_k(\vf{r}, a)
            %    &= \sum_{m \neq k}^N
            %    \Biggl[
            %        \frac{1}{r_{km}^2(r_{km} - a)}
            %        - \frac{r_{km} - 1}{r_{km}^2(r_{km} - a)^2}
            %    \Biggr] \\
            %    &=
            %    \sum_{m \neq k}^N
            %    \frac{1 - a}{r_{km}^2(r_{km} - a)^2}, \\
            %    \vfg{\zeta}_k(\vf{r}, a)
            %    &=
            %    \sum_{m \neq k}^N
            %    \frac{\vf{r}_k - \vf{r}_m}{r_{km}^2(r_{km} - a)}.
            %\end{align}
            %We can then rewrite the expression for the Laplacian to
            %    \begin{align}
            %        \frac{\nabla_k^2\bra{\vf{r}}\ket{\Psi_T}}
            %        {\bra{\vf{r}}\ket{\Psi_T}}
            %        &=
            %        -2\alpha
            %        \big(
            %            2 + \beta
            %        \bigr)
            %        + 4\alpha^2
            %        \bigl(
            %            x_k^2 + y_k^2 + \beta^2z_k^2
            %        \bigr)
            %        %\nonumber \\
            %        %&\qquad
            %        +
            %        2a\xi_k(\vf{r}, a)
            %        \nonumber \\
            %        &\qquad
            %        -4a\alpha(x_k\vf{e}_i + y_k\vf{e}_j + \beta z_k\vf{e}_k)
            %        \cdot
            %        \vfg{\zeta}_k(\vf{r}, a)
            %        + a^2\vfg{\zeta}_k(\vf{r}, a)^2.
            %    \end{align}
            %    Both $\xi_k$ and $\vfg{\zeta}_k$ can be evaluated in a common
            %    loop. Using this expression for the Laplacian we can find the
            %    local energy from
            %    \begin{align}
            %        E_L(\vf{r})
            %        &=
            %        \frac{\bra{\vf{r}}H\ket{\Psi_T}}
            %        {\bra{\vf{r}}\ket{\Psi_T}}
            %        =
            %        \sum_{k}^N
            %        \Biggl(
            %            -\frac{\hbar^2}{2m}
            %            \frac{\nabla_k^2\bra{\vf{r}}\ket{\Psi_T}}
            %            {\bra{\vf{r}}\ket{\Psi_T}}
            %            + V_{\text{ext}}(\vf{r})
            %        \Biggr)
            %        +
            %        \sum_{i < j}^N w(\vf{r}_i, \vf{r}_j).
            %    \end{align}

>>>>

\documentclass[
    a4paper, aps, twocolumn, floatfix, superscriptaddress, nofootinbib]{revtex4-1}

@@

\begin{abstract}
    Something very abstract and clever should go here.
    \begin{figure}[h!]
	\centering
	\includegraphics[width=0.7\textwidth]{loopholes.jpg}
\end{figure}
\end{abstract}

@@

        \subsubsection{Non-interacting harmonic oscillator}
            We start by finding an analytical expression for the local energy in
            a system where we set $a = 0$ and $\beta = 1$, i.e., a system of
            non-interacting harmonic oscillators.
            \begin{align}
                \Psi_T(\vf{r})
                = \Phi_T(\vf{r})
                = \prod_i^N \exp\bigl[
                    -\alpha |\vf{r}_i|^2
                \bigr],
            \end{align}
            where $|\vf{r}_i| = r_i$. As $a = 0$ the interaction term,
            $w(\vf{r}_i, \vf{r}_j)$, vanishes and the Hamiltonian is given by
            (in the spherical case)
            \begin{align}
                H &= \sum_i^N h(\vf{r}_i)
                = \sum_i^N \Biggl(
                    -\frac{\hbar^2}{2m}\nabla_i^2
                    + \half m \omega^2 r_i^2
                \Biggr).
            \end{align}
            The hardest part of finding the local energy is computing the
            kinetic term. Starting with the gradient of the wavefunction in the
            non-interacting case, we get
            \begin{align}
                \nabla_k\Psi_T(\vf{r})
                &= -2\alpha \vf{r}_k\Psi_T(\vf{r}).
            \end{align}
            The Laplacian yields
            \begin{align}
                \nabla^2_k\Psi_T(\vf{r})
                &= \big(-2d\alpha + 4\alpha^2 r_k^2\bigr)\Psi_T(\vf{r}),
            \end{align}
            where $d$ is the dimensionality of the problem determined by
            $\vf{r}_k \in \mathbb{R}^d$. This yields the analytical expression
            for the local energy in the non-interacting case to be
            \begin{align}
                E_L(\vf{r})
                &=
                \sum_i^N
                \Biggl(
                    -\frac{\hbar^2}{2m}
                    \bigl[
                        -2d\alpha + 4\alpha^2 r_i^2
                    \bigr]
                    + \half m\omega^2 r_i^2
                \Biggr).
            \end{align}
            In natural units, with $\hbar = c = m = 1$, this reduces to
            \begin{align}
                E_L(\vf{r})
                &=
                \alpha dN
                + \biggl(
                    \half\omega^2
                    - 2\alpha^2
                \biggr)
                \sum_i^N r_i^2.
            \end{align}
            It is worth noting that for $\alpha = \half\omega$ we will find a
            stable value. This happens as the entire sum over all the random
            walkers disappears.

@@

@@

@@

\section{Algorithms}

In the project we rely on a Monte Carlo approach of random sampling to obtain numerical results. 
Ironic, is it not? To rely randomness to solve problems that must be naturally deterministic? 
We simulate random walks over a volume in order to find optimal parameters in our trial wavefunctions. 
The most common of such methods, which we make use of herein, is the Metropolis-Hastings algorithm.

\subsection{Metropolis-Hastings Algorithm}
The Metropolis-Hastings algorithm can in our particular situation be condensed down to the following steps,
\begin{enumerate}
	\item The system is initialised by a certain number $N$ of randomly generated positions, or particles. This allows us to evaluate the
	 wavefunction at these points and compute the local energy $E_L$.
	\item The initial configuration is changed by setting a new position for one of these particles. The particle is picked at random.
	\item A ratio between new wavefunction density and the previous (initial) density is computed and compared to a random number. 
	This acceptance probability decides if the particle move is rejected or accepted. 
	The particle is only allowed to move a predetermined step length.
	\item If the particle movement is accepted and the local energy $E_L$ is computed for the new system. 
	\item Repeat steps until convergence and an optimum is reached.
\end{enumerate}

The algorithm described above can be applied in an "exhaustive" search of the parameter space in order to find the optimal parameters. 
Whether a proposed move is accepted or not is determined by a transition probability and the acceptance probability. 
The strength of the algorithm is that the transition algorithm need not be known.

\subsubsection{Importance Sampling}
A problem with the naïve Metropolis-Hastings sampling approach is that the sampling of the position space is done with 
no regard for where we are likely to find a particle. This problem can be remedied through a \emph{importance sampling}. 
It is reasonable to assume that the particles we erratically scatter in space are prone to movement towards the peaks 
of the probability density as dictated by the wave function. Consider therefore the Fokker-Planck equation,
\begin{equation}
	\frac{\partial \psi}{\partial t} = D \frac{\partial }{\partial x}\left(\frac{\partial }{\partial x} - F \right) \psi,	
	\label{eq:fokker_planck}
\end{equation}
which described the evolution in time of a probability density function, here exchanged for the wavefunction $\psi$. 
Originaly an equation that models diffusion, we have a diffusion term $D$ and a drift force, 
\begin{equation}
	F = \frac{2}{\psi} \frac{\partial \psi}{\partial x}.
\end{equation}

The one-particle model corresponding to the Fokker-Planck equation is the Langevin equation,
\begin{equation}
	\frac{\partial x}{\partial t} = D F(x) + \eta,
	\label{eq:langevin}
\end{equation}
where $\eta$ is a uniformly distributed stochastic variable. Solving Langevin's equation by Eurler's method gives a recursive relation for
the subsequent new positions of a particle,
\begin{equation}
	x_{t+\Delta t} = x_t + D F(x) \Delta t +\xi \sqrt{\Delta t},
\end{equation}
given a time step $\Delta t$\footnote{Bear in mind that \autoref{eq:langevin} is only valid as $\Delta t \to 0$, a property stemming from the use of Euler's method.} and a normally distributed stochastic variable $\xi$.

Now we need to change the acceptance probability of the metropolis algorithm to something that takes 
the new sampling method into account,
\begin{equation}
	q(x_{\text{new}}, x) = \frac{G(x, x_{\text{new}}, \Delta t)\abs{\psi_T(x_{\text{new}})}}{G(x_{\text{new}}, x, \Delta t)\abs{\psi_T(x)}}
\end{equation}
where $G$ is the Green's function to the Fokker-Planck equation,
\begin{align}
	G&(x_{\text{new}}, x, \Delta x) \nonumber \\
	&= \frac{1}{(4\pi D \Delta t)^{3N/2}}\exp\left(-\frac{(x_{\text{new}} - x - D\Delta t F(x))^2}{4D\Delta t} \right).
\end{align}
